### 2008-03-16 trunk/Papers/dl-gre-08/gre.tex
explained my algorithm

\begin{algorithm}[t]
\dontprintsemicolon
\caption{add$_\el$($C$, $\C$)}
\label{algo:bisim-add-el}
\For{$C' \in \C$ non-singleton}{
  \If{$C' \sqcap C$ is not subsumed in $\C$}{
    add $C' \sqcap C$ to $\C$ \;
    remove subsumed concepts from $\C$\;
  }
}
\end{algorithm}

>>>>

\begin{algorithm}[t]
\dontprintsemicolon
\caption{add$_\el$($C$, $\C$)}
\label{algo:bisim-add-el}
\For{$C' \in \C$ non-singleton}{
  \If{$C' \sqcap C$ is not subsumed in $\C$ {\bf and} 
    $\interp{C' \sqcap C} \neq \emptyset$ {\bf and}
    $\interp{C' \sqcap C} \neq \interp{C'}$}{
    add $C' \sqcap C$ to $\C$ \;
    remove subsumed concepts from $\C$\;
  }
}
\end{algorithm}
